XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler

### 2024-11-17 paper/main.tex
update paper & dataset
update paper

% !TEX root = C:\Users\xilua\My Drive\Workspace\llm_xpath\feilian\paper\main.tex
\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolceurws}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{adjustbox}
\usepackage{caption} % 引入 caption 包
\usepackage{hyperref}
% \usepackage[sort, authoryear]{natbib}

@@

\begin{abstract}
  We present XPath Agent, a production-ready XPath programming agent specifically designed for web crawling and web GUI testing. A key feature of XPath Agent is its ability to automatically generate XPath queries from a set of sampled web pages using a single natural language query. To demonstrate its effectiveness, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a range of web crawling tasks. Our results show that XPath Agent achieves comparable performance metrics while significantly reducing token usage and improving clock-time efficiency. The well-designed two-stage pipeline allows for seamless integration into existing web crawling or web GUI testing workflows, thereby saving time and effort in manual XPath query development.
\end{abstract}

@@

\section{Related Work}
\subsection{Generative Information Extraction}
Large Language Models (LLMs) are increasingly being used for generative information extraction (IE), where they directly generate structured knowledge from text—such as entities, relations, and events—offering an alternative to traditional discriminative methods (Xu et al., 2024). LLMs are especially advantageous in low-resource settings and support multitasking formats, which enhances their adaptability across various IE tasks. These tasks are typically categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with a rigorous comparison of models’ performance in each area (Xu et al., 2024).

@@

In our implementation, we prompt LLM to extract all information at once on a single page with JSON format. So, multiple fields or multiple values for a single field might be extracted. We treat all extracted values are relevant and passing them to the next stage.

@@

In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result.

@@

@@

\section{Information Extraction Prompt}
This is the first appendix.

\section{Program XPath Prompt}
This is the second appendix.

>>>>

% !TEX root = C:\Users\xilua\My Drive\Workspace\llm_xpath\feilian\paper\main.tex
\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolceurws}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{adjustbox}
\usepackage{caption} % 引入 caption 包
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{listings}
\usepackage[utf8]{inputenc}

@@

\begin{abstract}
  We present XPath Agent, a production-ready XPath programming agent specifically designed for web crawling and web GUI testing. A key feature of XPath Agent is its ability to automatically generate XPath queries from a set of sampled web pages using a single natural language query. To demonstrate its effectiveness, we benchmark XPath Agent against a state-of-the-art XPath programming agent across a range of web crawling tasks. Our results show that XPath Agent achieves comparable performance metrics while significantly reducing token usage and improving clock-time efficiency. The well-designed two-stage pipeline allows for seamless integration into existing web crawling or web GUI testing workflows, thereby saving time and effort in manual XPath query development. The source code for XPath Agent is available at \url{https://github.com/eavae/feilian}.
\end{abstract}

@@

\section{Related Work}
\subsection{Generative Information Extraction}

Large Language Models (LLMs) are increasingly being used for generative information extraction (IE), where they directly generate structured knowledge from text—such as entities, relations, and events—offering an alternative to traditional discriminative methods (Xu et al., 2024). LLMs are especially advantageous in low-resource settings and support multitasking formats, which enhances their adaptability across various IE tasks. These tasks are typically categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with a rigorous comparison of models’ performance in each area (Xu et al., 2024).

@@

In our implementation, we prompt LLM to extract all information at once on a single page with JSON format. So, multiple fields or multiple values for a single field might be extracted. We treat all extracted values are relevant and passing them to the next stage. The prompt for the Information Extraction stage is shown in Section \ref{sec:ie_prompt}.

@@

In our implementation, we limited the number of feedback loop to 3. At the end of the loop, we take the best XPath query based on evaluation result as the final result. The prompt for the Program XPath stage is shown in Section \ref{sec:program_xpath_prompt}.

@@

\clearpage
\onecolumn

@@

\centerline{\Large\bfseries Appendix}

\section{Information Extraction Prompt}
\label{sec:ie_prompt}

The prompt for the Information Extraction stage in the following format:

\begin{tcolorbox}
  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
Extract the information and cues from the given context that are required by the question, and present the results in JSON format. When presenting the results, ensure character-level consistency with the extracted text, do not make any modifications. The given context may be incomplete or may not have the answer, so, the final JSON conclusion must not include any fields that have not been mentioned.

When there are multiple similar expressions, prioritize them according to the following rules (from high to low):
1. The label of the target text is more important in HTML semantics.
2. The target text is completely within a tag, rather than within a sentence or paragraph.
3. The target text is closer to other fields to be extracted.
4. If these expressions can complement each other, please extract them all.

Cue Text (cue_text, from high to low):
1. Cue Text: In HTML, the indicative text that signals the upcoming extraction of the target text, such as `Phone number` or `Address:`.
2. When there is no cue text, use an empty string.

# Question:
{{ query }}

# Context:
```html
{{ context }}
```

# Answer Format (ignore the format requirements in the `Question`, strictly follow the answer format of cue_text and value):
Thought: ...(Your thoughts, about fields mentioned in the context and their cues)...
Conclusion: ...(Strictly follow the JSON example format to answer: {{ json_example }})...

# Your Answer:
\end{lstlisting}
\end{tcolorbox}

\section{Program XPath Prompt}
\label{sec:program_xpath_prompt}

The system prompt for the Program XPath stage in the following format:

\begin{tcolorbox}
  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
You are a pro software engineer, your task is reading the HTML code that user sent, and then response **one** Xpath (wrapped in JSON) that can recognize the element in the HTML to extract `target value`.

Here're some hints:
1. Do not output the xpath with exact value or element appears in the HTML.
2. Reference to the `target value` and the generated the xpath (if exists) to get more context.
3. When using text predication, always using `contains(., 'value')` instead of `text()='value'`.
4. If the target xpath ends with `text()[n]`, where n is not 1, please do not ignore it.
5. If cue text exist, using cue text and cue xpath to compose a new xpath might be a better idea.
6. String functions are allowed, such as `starts-with()`, `ends-with()`, `substring-before()`, `substring-after()`. Use it in caution, since it can only be used on `text()` node.

Please always response in the following Json format:
{
  "thought": "", # a brief thought of how to confirm the value and generate the xpath
  "xpath": "" # a workable xpath to extract the value in the HTML
}    
  \end{lstlisting}
\end{tcolorbox}

The feedback prompt for the Program XPath stage in the following format:

\begin{tcolorbox}
  \begin{lstlisting}[language={}, basicstyle=\ttfamily, columns=fullflexible, breaklines=true]
Following the feedbacks to refine the xpath you provided:

1. Extend the xpath to include the missing information if `Missing`.
2. Restrict the xpath to exclude the irrelevant information if `Surplus`.
3. Correct the xpath grammer if `Invalid`.
4. Response same xpath if no better solution.

{% for feedback in feedbacks %}
#### Evaluated on Fragment {{ feedback.id }}:
Extracted (JSON encoded): `{{ feedback.extracted | tojson }}`
Feedback Message: `{{ feedback.message }}`
{%- endfor %}    
  \end{lstlisting}
\end{tcolorbox}
